Improved Approximation Algorithms for the Maximum Carpool Matching Problem

### 2017-02-05 src/sub.tex
fix

Given a \carpool instance $(G = (V,A), c, w)$, consider a subset
$S \subseteq V$.  Let $M(S)$ be the maximum weight carpool matching
that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$,
namely $M(S)$ is the best carpool matching whose drivers belong to $S$
and whose passengers belong to $V \setminus S$.  In other words,
$M(S)$ is the maximum weight carpool matching that is a subset of
$A \cap (V \setminus S) \times S$.
%
Given $S$, the carpool matching $M(S)$ can be computed in polynomial
time using maximum flow as shown in~\cite{kutiel2016}.

Consider the function $\barw: 2^V \to \R$, where $\barw(S) \eqdf
w(M(S))$.  In the next lemma we prove that $\bar{w}$ is
a \emph{submodular set function}.  Recall that a function $f$ is
submdular if $f(S) + f(T) \geq f(S \cup T) + f(S \cap T)$ for every
two sets $S$ and $T$ in the domain of $f$.

@@

>>>>

Given a \carpool instance $(G = (V,A), c, w)$, consider a subset
$S \subseteq V$.  Let $M(S)$ be the maximum weight carpool matching
that satisfies $D_{M(S)} \subseteq S \subseteq V \setminus P_{M(S)}$,
namely $M(S)$ is the best carpool matching whose drivers belong to $S$
and whose passengers belong to $V \setminus S$.  In other words,
$M(S)$ is the maximum weight carpool matching that is a subset of
$A \cap (V \setminus S) \times S$.
%
Given $S$, the carpool matching $M(S)$ can be computed in polynomial
time using a maximum b-matching in the bipartite graph 
$B = (S \cup V \setminus S, A \cap (V \setminus S) \times S)$ or can be reduced
to a max-cost flow problem as shown in~\cite{kutiel2016}.

Consider the function $\barw: 2^V \to \R$, where $\barw(S) \eqdf
w(M(S))$.  In the next lemma we prove that $\bar{w}$ is
a \emph{submodular set function}.  Recall that a function $f$ is
submodular if $f(S) + f(T) \geq f(S \cup T) + f(S \cap T)$ for every
two sets $S$ and $T$ in the domain of $f$.

@@

\begin{figure}
\centering
\input{fig-submodular}
\caption[]{
\label{fig:defs}
In this example, $M$ is the set of the blue, dashed arcs, then:
$val_M(2) = 7$,
$val_M(3) = 2$,
$val_M(6) = 0$,
$\delta_M(2, 3) = 1$,
$\delta_M(6, 3) = 2$,
the set $\{(2,3), (6,3)\}$ is an \emph{improvement} to vertex 3,
$inc(2,3) = \{(1,2),(4,2),(3,5),(6,3)\}$,
$\text{pass}_M(2) = \{1, 4\}$.
}
\end{figure}
